Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.

### 2021-08-17 article/draft.tex
reference OANN in YT section

To illustrate the implementation of this policy we provide two examples for the temporary suspension of the following two YouTube channels: \href{https://www.youtube.com/channel/UCNbIDJNNgaRrXOD7VllIMRQ}{One America news Network} and \href{https://www.youtube.com/user/TonyHeller1}{Tony Heller}. The website of One America News Network has a ``low'' factual reporting score according to iffy.news.\footnote{See \href{https://mediabiasfactcheck.com/one-america-news-network/}{mediabiasfactcheck.com/one-america-news-network/}.}  Tony Heller posts regularly blog posts on the website {\it realclimatescience.com}, which also has a ``low'' factual reporting score according to iffy.news.\footnote{See \href{https://mediabiasfactcheck.com/real-climate-science/}{mediabiasfactcheck.com/real-climate-science/}} Both are active on YouTube and both have communicated via their Twitter account about restrictions applied by YouTube over their content (see figure \ref{fig2_oann}).

>>>>

To illustrate the implementation of this policy we provide two examples for the temporary suspension of the following two YouTube channels: \href{https://www.youtube.com/channel/UCNbIDJNNgaRrXOD7VllIMRQ}{One America news Network} and \href{https://www.youtube.com/user/TonyHeller1}{Tony Heller}. The website of One America News Network has a ``low'' factual reporting score according to iffy.news and several inaccurate articles according to feedback.org.\footnote{See \href{https://mediabiasfactcheck.com/one-america-news-network/}{mediabiasfactcheck.com/one-america-news-network/} and \href{https://open.feedback.org/media/AE6Q}{https://open.feedback.org/media/AE6Q}.}  Tony Heller posts regularly blog posts on the website {\it realclimatescience.com}, which also has a ``low'' factual reporting score according to iffy.news.\footnote{See \href{https://mediabiasfactcheck.com/real-climate-science/}{mediabiasfactcheck.com/real-climate-science/}} Both are active on YouTube and both have communicated via their Twitter account about restrictions applied by YouTube over their content (see figure \ref{fig2_oann}).
